Measuring causal influence with\\ back-to-back regression

### 2019-05-22 paper/meg_exps.tex

% \paragraph{Back-to-back regression} We adapted back-to-back regression with two
% changes. First, to avoid getting a slightly positively-biased estimate of the
% factors contributing to the MEG signal, we swap the Tikhonov regularization of
% the first regression $G$ with a truncated regularization. Truncation was fitted
%  by maximum likelihood estimate, as implemented in scikit-learn principal
%  component analysis. Second, to minimize the variance increase induced by
%  bagging, we computed the inverse regularized covariance matrices outside
%  bagging:
% \begin{equation}
%   G = (Y^T Y+\lambda_Y I)^{-1} Y_{train}^T X_{train}
% \end{equation}
% \begin{equation}
% \hat X_{test} = Y_{test} \cdot G^T
% \end{equation} where $\left(train,test\right)$ are partitions of the data.

@@

The three types of analyses were implemented for each subject and each time
sample independently.  To estimate the reliability of these estimates in the
population, we tested, using one-sample $t$-test whether the distribution of
the estimated contribution of each factor different from baseline ($t=-100$ms),
as $\text{t-test}(\hat E_{t=-100} - \hat E_{\tau})$, with $\tau \in $ 150ms and
400ms respectively

@@

We aimed to estimate

We show these coefficients as a function of time in the stacked plots, in Figure
\ref{fig:megresult}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{Average magnetosensor response across words for one subject.}
  \label{fig:megresult}
\end{figure}

>>>>

%<<<<<<< HEAD
% \paragraph{Back-to-back regression} We adapted back-to-back regression with two
% changes. First, to avoid getting a slightly positively-biased estimate of the
% factors contributing to the MEG signal, we swap the Tikhonov regularization of
% the first regression $G$ with a truncated regularization. Truncation was fitted
%  by maximum likelihood estimate, as implemented in scikit-learn principal
%  component analysis. Second, to minimize the variance increase induced by
%  bagging, we computed the inverse regularized covariance matrices outside
%  bagging:
% \begin{equation}
%   G = (Y^T Y+\lambda_Y I)^{-1} Y_{train}^T X_{train}
% \end{equation}
% \begin{equation}
% \hat X_{test} = Y_{test} \cdot G^T
% \end{equation} where $\left(train,test\right)$ are partitions of the data.

@@

The three types of analyses were implemented for each subject and each time
sample independently.  To estimate the reliability of these estimates in the
population, we tested, using one-sample $t$-test whether the distribution of
the estimated contribution of each factor different from baseline ($t=-100$ms),
as $\text{t-test}(\hat E_{t=-100} - \hat E_{\tau})$, with $\tau \in $ 150ms and
400ms respectively
% =======
% \paragraph{Back-to-back regression} We adapted back-to-back regression with two
% changes. First, to avoid getting a slightly positively-biased estimate of the
% factors contributing to the MEG signal, we swap the Tikhonov regularization of
% the first regression $G$ with a truncated regularization. Truncation was fitted
%  by maximum likelihood estimate, as implemented in scikit-learn principal
%  component analysis. Second, to minimize the variance increase induced by
%  bagging, we computed the inverse regularized covariance matrices outside
%  bagging:
% \begin{equation}
%   G = (Y^T Y+\lambda_Y I)^{-1} Y_{train}^T X_{train}
% \end{equation}
% \begin{equation}
% \hat X_{test} = Y_{test} \cdot G^T
% \end{equation} where $\left(train,test\right)$ are partitions of the data.
% %
% % \subsubsection{Second-level statistics}
% %
% % The three types of analyses were implemented for each subject and each time
% % sample independently.  To estimate the reliability of these estimates in the
% % population, we tested, using one-sample $t$-test whether the distribution of
% % the estimated contribution of each factor different from baseline ($t=-100$ms),
% % as $\text{t-test}(\hat E_{t=-100} - \hat E_{\tau})$, with $\tau \in $ 150ms and
% % 400ms respectively
% >>>>>>> 1775190a9737244f84b8ace529198a443029ad8d

@@

We show all the feature coefficients as a function of time in the stacked plots,
Figure \ref{fig:megresult}. Our method confirms previous findings in
neuroscience literature. In particular, \cite{kutas2011thirty} find that word
frequency correlates with a brain wave around 400ms. Similarly,
\cite{pegado2014timing} show that letter strings correlate with early brain
responses. Both these phenomena can be observed in Figures
\ref{fig:meg_twocurves} and \ref{fig:megresult}, where we show that our
method is able to separate them more clearly than the forward regression
approach.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{We plot the coefficients corresponding to each of the features,
  describing their importance over time after stimuli onsets. We can observe that visual features start peaking around 150ms, while lexical features peak around 400ms. We show a similar plot for the Ridge regression baseline (forward) in Figure \ref{fig:ridgebaselineresult}.}
  \label{fig:megresult}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/ridgecv_baseline_result.pdf}
  \caption{Ridge regression baseline. All the coefficients appear to be
  linearly correlated, unlike our method in Figure \ref{fig:megresult}.}
  \label{fig:ridgebaselineresult}
\end{figure}
